msprime 1.0: an efficient and extensible coalescent simulation framework

### 2021-07-15 paper.tex
Comment out png includes
Point out the ancestry/mutation distinction
And outline the subsections below

In this section we describe the main features of \msprime\ 1.0.

@@

\begin{figure}
\begin{center}
\begin{tabular}{cc}
\includegraphics[width=5cm]{msprime-scaling.png} &
\includegraphics[width=5cm]{figures/recombination} \\
\end{tabular}
\end{center}
% \includegraphics[width=\textwidth]{figures/recombination}
\caption{\label{fig-recombination-perf}(A) Approximate run time for \msprime\
simulations as a function of scaled recombination rate.
(B) Comparison of the ARG simulations vs minimal tree sequence representation.}
\end{figure}

@@

\begin{figure}
\begin{center}
\includegraphics[width=6cm]{simbac.png}
\end{center}
\caption{\label{fig-gc-perf}Comparison of the running time
for E-coli simulations using \msprime\ and SimBac for varying
sample sizes. The parameters used are [] based on [references].}
\end{figure}

@@

\begin{figure}
\begin{center}
\includegraphics[width=6cm]{msprime-argon-runtimes.png}
\end{center}
\caption{\label{fig-dtwf-perf} Comparison of \msprime's DTWF
simulations with ARGON. To ensure the comparison with ARGON is
as fair as possible we run it with a mutation rate of 0 and with
the minimum output options (so that it writes out only an empty VCF file)}
\end{figure}

>>>>

In this section we describe the main features of \msprime\ 1.0. Methodologically,
there exists a logical separation between simulating coalescent genealogies and
adding neutral mutations onto these genealogies. Simulating genetic ancestry
requires methods that model the underlying reproductive process (e.g. Moran,
Wright-Fisher, etc.) as well as accounting for recombination of various sorts
(including gene conversion), demography, and selection. These methods are
discussed in the first N subsections below. One of the strengths of the
approach taken in msprime is that neutral mutations can be retrospectively
added to simulated genealogies. Methods to generate mutations, and thereby
generate genetic variation, are therefore discussed in a separate and subsequent
subsection. Finally, we describe the \msprime\ API, which is designed to enforce
the distinction between simulating genealogies and mutations; discuss the
interoperability provided by the use of \tskit\, the tree sequence toolkit;
and highlight the open source development process which allows for \msprime\
to be extended by addition of new features while ensuring robustness and
maintainability of the core codebase.

@@

\begin{figure}
% \begin{center}
% \begin{tabular}{cc}
% % \includegraphics[width=5cm]{msprime-scaling.png} &
% % \includegraphics[width=5cm]{figures/recombination} \\
% \end{tabular}
% \end{center}
\includegraphics[width=\textwidth]{figures/recombination}
\caption{\label{fig-recombination-perf}(A) Approximate run time for \msprime\
simulations as a function of scaled recombination rate.
(B) Comparison of the ARG simulations vs minimal tree sequence representation.}
\end{figure}

@@

\begin{figure}
\begin{center}
% \includegraphics[width=6cm]{simbac.png}
\end{center}
\caption{\label{fig-gc-perf}Comparison of the running time
for E-coli simulations using \msprime\ and SimBac for varying
sample sizes. The parameters used are [] based on [references].}
\end{figure}

@@

\begin{figure}
\begin{center}
% \includegraphics[width=6cm]{msprime-argon-runtimes.png}
\end{center}
\caption{\label{fig-dtwf-perf} Comparison of \msprime's DTWF
simulations with ARGON. To ensure the comparison with ARGON is
as fair as possible we run it with a mutation rate of 0 and with
the minimum output options (so that it writes out only an empty VCF file)}
\end{figure}
